Northern Pikeminnow Predation on Juvenile Chinook Salmon and Potential Impacts to Local Populations

### 2021-12-03 analysis/paper/paper.Rmd
added psd calculation

@@

where $FQ_{i}$ is the number of fish $\ge$ quality-length for species $i$, and $FS_{i}$ is the number of fish $\ge$ stock-length for species $i$. We calculated the PSD for Northern Pikeminnow in our study using 300 mm TL for stock-size and 400 mm TL for quality-size.

@@

The PSD for Northern Pikeminnow in our study and across all three years was 42.3%. In other words, 42.3% of captured fish were over the quality size classification of 400 mm TL, demonstrating that a high percentage of Northern Pikeminnow within Deadwater Slough are above average size classes defined for the species <!-- Is this useful? And if useful, does it make sense to calculate PSD separately for the fall and spring periods? I'd expect PSD to vary between seasons. -->

>>>>

```{r psd}
s_size = 300
q_size = 400

psd_df = cmr_df %>%
  select(species, count, length, recap, event_name) %>%
  filter(recap  != TRUE)

fs = psd_df %>%
  filter(length >= s_size) %>%
  nrow()

fq = psd_df %>%
  filter(length >= q_size) %>%
  nrow()

psd = 100 * (fq/fs)

@@

where $FQ_{i}$ is the number of fish $\ge$ quality-length for species $i$, and $FS_{i}$ is the number of fish $\ge$ stock-length for species $i$. We calculated the PSD for Northern Pikeminnow in our study using `r prettyNum(s_size, digits = 0)` mm TL for stock-size and `r prettyNum(q_size, digits = 0)` mm TL for quality-size.

@@

The PSD for Northern Pikeminnow in our study and across all three years was `r prettyNum(psd, digits = 1)`%. In other words, `r prettyNum(psd, digits = 1)`% of captured fish were over the quality size classification of `r prettyNum(q_size, digits = 0)` mm TL, demonstrating that a high percentage of Northern Pikeminnow within Deadwater Slough are above average size classes defined for the species <!-- Is this useful? And if useful, does it make sense to calculate PSD separately for the fall and spring periods? I'd expect PSD to vary between seasons. -->
